### 2020-05-03 thesis_template/3_Body/model/access_own_reference_slice.tex
docu
conclusion done

This experiment is conducted to understand two questions. One is how different variable types have impact to runtime performance.
The other is how initialization of Vec size has impact to runtime performance. 
In this experiment, we focus on owner, reference, and slice as a variable of sequence values. 
Since these variables have different memory representation, there might be differences among time for access to actual values of each variables.

@@

Next, 1.5, 1.8, 2.5, 2.8, 3.5, and 3.8 million of Customer objects are created and stored in Vec. 
When a Customer Vec is created, whether size of Vec is initialized is controlled. 
Finally, serialization of Customer object is performed as an operation forcing program to access all of fields in the object.
This serialization is performed each Customer objects in the Vec. We measure total runtime to serialize all of Customer objects 
stored in Vec.

@@

No matter Vec size initialized or not, differences of runtime for accessing objects are not remarkable among different object types. 
The percent increase in runtime of accessing to fields of from 1.5 to 3.8 million CustomerOwned objects is 121\% if the Vec is initialized, 554\% if the Vec is not initialized.

Considering the differences of percent increase of runtime whether the Vec is initialized or not, 
Figure\ref{fig:init_vs_noinit} the comparison of runtime access to fields of CustomerOwned object with and without Vec Initialization.
For 3.8 million of objects, the difference of runtime to access to the objects is 38745 secounds; program without Vec initialization is 60\% slower than one with the initialization.

@@

\begin{figure}[htb]
    \includegraphics[width=15cm]{rust_access_init_vs_noint.eps}
    \caption{Runtime of Access to Fields of Complex Object with Initialization vs without Initialization}
    \label{fig:init_vs_noinit}
\end{figure}

@@

Whether initializing Vec size results in disparity of runtime performance to access objects' fields. 
This is because when Vec uninitialized, the elements of Vec are allocated across different virtual memory pages.

>>>>

This experiment is conducted to provide answers to the following two questions. One is how different variable types have impact to runtime performance.
The other is how initialization of Vec size has impact to runtime performance. 
In this experiment, we focus on owner, reference, and slice as a variable of sequence values. 
Since these variables have different memory representation, there might be differences among time for access to actual values of each variables.

@@

Next, 3, 13, 23, 33 million of Customer objects are created and stored in Vec. 
When a Customer Vec is created, whether size of Vec is initialized is controlled. 
Finally, serialization of Customer object is performed as an operation forcing program to access all of fields in the object.
This serialization is performed each Customer objects in the Vec. We measure total runtime to serialize all of Customer objects 
stored in Vec.

@@

No matter Vec size initialized or not, differences of runtime for accessing objects are not remarkable among different object types.

@@

% \begin{figure}[htb]
%     \includegraphics[width=15cm]{rust_access_init_vs_noint.eps}
%     \caption{Runtime of Access to Fields of Complex Object with Initialization vs without Initialization}
%     \label{fig:init_vs_noinit}
% \end{figure}

@@

% Whether initializing Vec size results in disparity of runtime performance to access objects' fields. 
% This is because when Vec uninitialized, the elements of Vec are allocated across different virtual memory pages.

### 2020-05-03 thesis_template/3_Body/model/experimental_set_detail.tex
conclusion done

 \subsection{Experimental Details}
 \label{sec:concept_expdetail}
 Our experiments are run on three types of VM instances on Google Cloud Platform: 
 n1-standard-1 which has 1 vCPU, 3.75 GB RAM, and 10 GB Standard persistent disk, 
 n1-standard-4 which has 4 vCPU, 15 GB RAM, and 10 GB Standard persistent disk, 
 n1-standard-8 which has 8 vCPU, 30 GB RAM, and 10 GB Standard persistent disk,  
 All of the experiments described are performed 5 times. 
 In this thesis, we present the average of 5 separate runs for each experiment.

>>>>

 \subsection{Experimental Details}
 \label{sec:concept_expdetail}
 Our experiments are run on VM instances on Google Cloud Platform, 
 n1-standard-8 which has 8 vCPU, 30 GB RAM, and 10 GB Standard persistent disk.
 In this thesis, we present the average of 5 separate runs for each experiment.

### 2020-05-03 thesis_template/3_Body/model/merge_sort_experiment.tex
conclusion done

We use scope method from crossbeam crate to perform multithread programming. 
Scoped thread can have reference to value from its parent thread by ensuring children threads are joined before their parent thread returns value. 
By using scoped thread, we can implement two merge-sort algorithms in identical way except whether the function receives Arc or reference of source vector.
The representations of source vector for each algorithm are shown in Figure~\ref{fig:source_merge_sort}.
The elements of source vector are CustomerOwned objects. We generates source vectors in size of 1, 2, 3 and 4 million.
Finally, merge-sort is performed based on value of key field. The figure shows the result for runtime performance of merge-sort algorithms on difference size of vectors. 
This experiment is run on n1-standard-4 and generates 4 threads to perform multithreading.

@@

\subsection{Result}
Figure~\ref{fig:source_merge_sort} shows the runtime performance of our merge-sort algorithm with specified Vec sizes. 
The blue and yellow bar charts represent the runtime performance of merge-sort algorithm using reference and Arc respectively. 
The result says that algorithms with Arc is about 24\% slower than algorithms with reference.

>>>>

We use scope method from crossbeam crate to perform multithread programming. 
Scoped thread can have reference to value from its parent thread by ensuring children threads are joined before their parent thread returns value. 
By using scoped thread, we can implement two merge-sort algorithms in identical way except whether the function receives Arc or reference of source vector.
The representations of source vector for each algorithm are shown in Figure~\ref{fig:source_merge_sort}.
The elements of source vector are CustomerOwned objects. We generates source vectors in size of 4, 8, 12 and 16 million.
Finally, merge-sort is performed based on value of key field. The figure shows the result for runtime performance of merge-sort algorithms on difference size of vectors.

@@

\subsection{Result}
Figure~\ref{fig:source_merge_sort} shows the runtime performance of our merge-sort algorithm with specified Vec sizes. 
The blue and yellow bar charts represent the runtime performance of merge-sort algorithm using reference and Arc respectively. 
The result says that algorithms with Arc is about 21\% slower than algorithms with reference.

### 2020-05-03 thesis_template/3_Body/model/tree_aggregate_experiment.tex
conclusion done

Numbers of CustomerOwned objects aggregated in our experiment are 1, 2, 3, 4 million. 
This experiment is run on n1-standard-4.

@@

\subsection{Result}
Figure~\ref{fig:ex_tree_agg} shows runtime performance of two tree-aggregate algorithms. 
The runtime of algorithm with deep-copy is about 33\% slower than algorithm with Arc for every vector size.

>>>>

Numbers of CustomerOwned objects aggregated in our experiment are 2, 4, 6, 8 million.

@@

\subsection{Result}
Figure~\ref{fig:ex_tree_agg} shows runtime performance of two tree-aggregate algorithms. 
The runtime of algorithm with deep-copy is about 40 to 50\% slower than algorithm with Arc for every vector size.

### 2020-05-03 thesis_template/4_Conclusion/conclusion.tex
conclusion done

\section{Summary of the thesis}

Time to get philosophical and wordy.

IMPORTANT: In the references at the end of thesis, all journal names must be
spelled out in full, except for standard abbreviations like IEEE, ACM, SPIE,
INFOCOM, ...

>>>>

% Quick recap of what we did 
% - The purpose of this research
% - Experiment that we conducted
In this thesis, we have presented a number of experiments to assess better implementation of algorithms 
when one develops Big Data analysis tools with Rust programming. 
Those experiments examine how different variable types, Reference Count (Rc), and different memory management strategies in Rust affect performance of algorithms.

% What we find 
% - The result of our experiments
The results show useful benchmark when one implements Big Data analysis tools.
The different variable types in Rust have similar access time to the memory address of their value. 
Therefore, we do not need to consider such access overheads. 
The drop on Rc or Arc is more expensive than ordinal variables, 
because these shared variables need to check count of reference to its actual value. 
The atomic operation used by Arc may be a cause of overhead in multithread programming in Rust.

% What is the most significant
% - Use of Reference is depending on Complex object type
% - When we have complex object, we should use Reference count
% - Frequency of memory de/allocation has impact
One of the most notable discussion is selection of whether developers should use sharing (Rc or Arc) or deep-copy. 
In algorithms used to process Big Data, the same elements are used over and over agin. 
In Experiment 4 and 5, we implement the algorithms in different strategies and assess which implementations performs better in runtime.
The result is that the algorithms sharing elements using Arc is more efficient strategy when the shared elements are very complex objects. 
On the other hand, when the elements have light complexity, such as String, the algorithms deep-copying the elements is more faster.
Therefore, the decision of which strategy to use is dependent on how complex element objects are.

% Conclusion acquired from that
% - the design of algorithm is depend on implemetation of complex objects
% - Rust ownership memory management seem to work well
% - We can manually de/allocate memory and compiler can still ensure memory safety.
The other important discussion is how Rust ownership memory management can impact performance of algorithm.
Even though the main concept of ownership is safety of memory, programming patterns using this ownership may determine the frequency and timing of de/allocation. 
Experiment 5 shows the ownership memory management works well; the frequency and timing of de/allocation is fairly reasonable for algorithms to result good runtime performance and memory usage. 
However, when the situation is memory intensive and needs more fast runtime performance, developers need to perform more careful memory managements,such as manually specifying when to deallocate memory.
Rust can check memory-safety of these manual operation at compile time, so such optimizations can be done fairly easy.

% How our conclusion can be applied in real world 
% - Decide data structure implementation that used in Big Data Systems then
% conduct experiment that fits for the best runtime performance.
As we can see in the results of experiment, different memory strategy varies the performance of algorithms in Rust programming.
Which memory management strategy to take depends on what objects to deal with. 
Therefore, development of Big Data analysis tools in Rust programming should be started with objects implementation used in the systems.
Next, one can select suitable memory management strategies. 
Finally, algorithms can be optimized with more dedicated strategies to application setting, such as capacity of memory.
